Create Regression Data

### 2022-05-10 data-cleaning/00-scrape-amicus-text.Rmd
add litigant frames

@@

```{r}
amicus_file_ids <- amicus_file_ids %>% 
  mutate(file_type = tolower(sub(".*\\.", "", name))) 
amicus_file_ids %>% group_by(file_type) %>% summarize(n = n())
```

@@

>>>>

If only getting specific folder, change here

```{r}
#case_folders <- case_folders %>% filter(case == "Gonzales v PP")
```

@@

```{r}
amicus_file_ids <- amicus_file_ids %>% 
  mutate(file_type = tolower(sub(".*\\.", "", name))) 
amicus_file_ids %>% group_by(file_type) %>% summarize(n = n())
```
Scrape text

@@

If adding in briefs, run below

```{r}
#full <- box_read("1029611016764")
#full <- full %>% rbind(amicus_txt) %>% arrange(case)
```

### 2022-05-10 data-cleaning/00b-scrape-litigant-text.Rmd
add litigant frames

There are ~40 folders in Supreme Court > Sup Ct - Abortion Cases. For each amicus file (NOT denoted by files with "amicus”, “amici”, “decision”, “reply”, “appendix”, and “oral” in the file name), copy the file ID, file name, case name, and file text into a CSV.

@@

  # in each case folder, grab the name and id of the decision file
  file_ids <-
    foreach(i = it,
            .combine = rbind,
            .inorder = F) %dopar% {
              i %>%
                filter(!grepl("amicus|amici|decision|reply|appendix|oral", name, ignore.case = T)) %>%
                select(case, name, id)
            }
  print("Obtained litigant file ids")

@@

```{r}
# save this file to data > processed amicus files
litigant_file_ids %>% 
  right_join(., case_folders, "case") %>% 
  group_by(case) %>% 
  summarize(n = sum(!grepl("amicus|amici|decision|reply|appendix|oral", name, ignore.case = T))) %>% 
  arrange(case) #%>% 
  #box_write(., "amicus brief counts.xlsx", dir_id = "145990409196")
```

Save list of amicus file IDs on Box

```{r}
# amicus_file_ids %>% 
#   right_join(., case_folders, "case") %>% 
#   select(-id.y) %>% 
#   rename(id = id.x) %>% 
#   mutate(file_type = tolower(sub(".*\\.", "", name))) %>% 
#   box_write(., "amicus-file-ids.csv", dir_id = "145990409196")
```

@@

```{r}
litigant_file_ids <- litigant_file_ids %>% 
  mutate(file_type = tolower(sub(".*\\.", "", name))) 
litigant_file_ids %>% group_by(file_type) %>% summarize(n = n())
```

```{r}
litigant_file_ids <- litigant_file_ids %>% filter(file_type == 'docx' | file_type == 'pdf')
```

@@

# get text of cases in parallel
amicus_txt <- foreach(i = itd, .inorder = F, .combine = rbind) %dopar% {

@@

@@

```{r}
# amicus_txt %>% 
#   mutate(txt_full = str_squish(txt_full),
#          summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
#   group_by(summary) %>% 
#   summarize(n=n())
```

Which files do not? -- should just be the 3 that we have manual adjustments recorded for.

```{r}
# amicus_txt %>% 
#   mutate(txt_full = str_squish(txt_full),
#          summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
#   filter(!summary) %>% 
#   select(brief)
```

Final column names

```{r}
amicus_txt %>% colnames()
```

@@

```{r}
box_write(amicus_txt,
          file_name = "raw-litigant-brief-text.csv",
          dir_id = '145990409196')
```

>>>>

There are ~40 folders in Supreme Court > Sup Ct - Abortion Cases. For each litigant file (NOT denoted by files with "amicus”, “amici”, “decision”, “reply”, “appendix”, and “oral” in the file name), copy the file ID, file name, case name, and file text into a CSV.

@@

  # in each case folder, grab the name and id of the decision file
  file_ids <-
    foreach(i = it,
            .combine = rbind,
            .inorder = F) %dopar% {
              i %>%
                filter(!grepl("amicus|amici|decision|reply|appendix|oral", name, ignore.case = T)) %>%
                select(case, name, id, type)
            }
  print("Obtained litigant file ids")

@@

```{r}
# save this file to data > processed amicus files
litigant_file_ids %>% 
  right_join(., case_folders, "case") %>% 
  group_by(case) %>% 
  summarize(n = sum(!grepl("amicus|amici|decision|reply|appendix|oral", name, ignore.case = T))) %>% 
  arrange(case)
```

Save list of litigant file IDs on Box

```{r}
#litigant_file_ids %>% 
  # only files
#  filter(type == "file", name != ".DS_Store") %>% 
  # add matching case
#  right_join(., case_folders, "case") %>% 
  # rename ids/type
#  select(-id.y, -type.y) %>% 
#  rename(id = id.x, type = type.x) %>% 
  # name lower
#  mutate(file_type = tolower(sub(".*\\.", "", name))) %>% 
  # select final vars
#  select(case, id, name, type) %>% 
#  arrange(case) %>% 
#  box_write(., "litigant-brief-file-ids.xlsx", dir_id = "162588272045")
```

@@

```{r}
litigant_file_ids <- litigant_file_ids %>% 
  mutate(file_type = tolower(sub(".*\\.", "", name))) 
litigant_file_ids %>% group_by(file_type) %>% summarize(n = n())
```
Filter for only pdf and docx files

```{r}
litigant_file_ids <- litigant_file_ids %>% filter(file_type == 'docx' | file_type == 'pdf')

# filter for only briefs that need to be re-pulled
litigant_file_ids <- litigant_file_ids %>% 
  filter(id %in% c("955405762992", "955404304453", "955405038378", "955401734984", "56699188926", "56701967150","56698341318"))
```

Read text

@@

# get text of cases in parallel
litigant_txt <- foreach(i = itd, .inorder = F, .combine = rbind) %dopar% {

@@

Read in list of litigant file IDs, drop those that are marked "drop"

```{r}
drop_file_ids <- box_read("955323576728") %>% 
  filter(drop == 1, !is.na(id)) %>% 
  select(id)

litigant_txt <- litigant_txt %>% filter(!(id %in% drop_file_ids$id))
```

@@

```{r}
litigant_txt %>% 
   mutate(txt_full = str_squish(txt_full),
          summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
   group_by(summary) %>% 
   summarize(n=n())
```

Which files do not? -- should just be the 3 that we have manual adjustments recorded for. These have been manually changed/corrected.

```{r}
 litigant_txt %>% 
   mutate(txt_full = str_squish(txt_full),
          summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
   filter(!summary) %>% 
   select(brief)
```

Add column for party

```{r}
litigant_txt <- litigant_txt %>% 
  mutate(brief_party = ifelse(grepl("\\(feminist\\)", brief, ignore.case=T), 1, 0)) %>% 
  select(case:id, brief_party, txt_full)
```

Check colnames 
```{r}
litigant_txt %>% colnames()
```

If adding cases adhoc, join now

```{r}
litigant_all <- box_read("955333134918") %>%
  filter(!(brief %in% c("Bellotti v Baird (1976). Brief for Appellees (feminist).docx",
                       "Colautti v. Franklin. Brief for Respondent (Feminist) - (labeled Beal v Franklin).pdf",
                       "Doe v. Bolton Brief for Petitioners (Feminist).pdf",
                       "Doe v. Bolton Brief for Respondents.pdf",
                       "H.L. v Matheson. Brief for Appellant (feminist).docx",
                       "United States v Vuitch. Brief for Appellant %28United States%29.docx",
                       "United States v. Vuitch. Brief for Respondent (Feminist).pdf"))) %>% 
  rbind(litigant_txt)
```

@@

```{r}
box_write(litigant_txt,
          file_name = "raw-litigant-brief-text.csv",
          dir_id = '162588272045')
```

### 2022-05-10 data-cleaning/01b-shorten-litigant-text.Rmd
add litigant frames

---
title: "Shorten Amicus Text"
author: "Sarah Torrence and Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

# data
# data/processed amicus files/raw-amicus-brief-text.csv
amicus <- box_read("863216279471")
# data/processed amicus files/amicus summary.xlsx
alternate_rmv <- box_read("864995408351", sheet = "data") %>% 
  select(case, brief, id, alternative) %>% 
  filter(!is.na(alternative))
#data/processed amicus files/footnotes-confirmed.csv
footnotes_ids <- box_read("908607927934")
```

@@

To pare down amicus text by removing unnecessary/irrelevant text.

@@

For most documents, there exists the header "summary of argument." If it did not exist, it was manually entered into the document. This represents the point at which the brief starts discussing their argument. We don't need text prior to this, as it's mainly intro information about the case and/or the authors. If "summary of argument" text doesn't exist (only in the case of a few pdfs), use the `alternative_rmv` df to find where to start reading the text.

alternate removal strings

```{r}
#alternate_rmv %>% select(id,alternative)
```

Remove text before summary of argument (already done in shortened-amicus-text csv, not raw text csv.)

```{r}
# remove text after "summary of argument" if it exists
amicus <- amicus %>%
  mutate(txt_full = str_squish(txt_full),
         txt_short = case_when(
           id == 861820795454 ~ gsub(pattern = ".*summary \\[\\*9\\] of the argument", replacement = "",
                                     x = txt_full, ignore.case = TRUE),
           grepl("summary of argument|Summary of Argument|SUMMARY OF ARGUMENT", txt_full,
                 ignore.case = TRUE) ~
             gsub(pattern = ".*summary of argument|.*Summary of Argument|.*SUMMARY OF ARGUMENT",
                  replacement = "",
                  x = txt_full, ignore.case = TRUE),
           grepl("summary of the argument", txt_full, ignore.case = TRUE) ~
             gsub(pattern = ".*summary of the argument", replacement = "",
                  x = txt_full, ignore.case = TRUE),
           id == 861820908073 ~ gsub(pattern = ".*introduction and summary", replacement = "",
                                     x = txt_full, ignore.case = TRUE),
           id == 861820896073 ~ gsub(pattern = ".*introduction", replacement = "",
                                     x = txt_full, ignore.case = TRUE),
           id == 861822667487 ~ gsub(pattern = ".*introduction", replacement = "",
                                     x = txt_full, ignore.case = TRUE),
           T ~ ''),
         txt_short = str_squish(txt_short))
```

@@

```{r}
amicus %>% filter(txt_short == "") %>% select(-txt_full)
```

@@

```{r}
#amicus %>% sample_n(1) %>% pull(txt_short)
```

@@

```{r}
amicus <- amicus %>%
  mutate(txt_short = str_squish(txt_short),
    appendix_1a = str_count(txt_short, "\\*1a Appendix|\\*1A APPENDIX|\\*1A Appendix|\\*IA APPENDIX"))
```

@@

```{r}
table(amicus$appendix_1a)
```

@@

```{r}
amicus <- amicus %>% mutate(
         txt_short = str_squish(txt_short),
         txt_short = case_when(
           grepl("\\*1a appendix|\\*ia appendix", txt_short, ignore.case = TRUE) ~ 
             gsub(pattern = "\\*1a appendix.*|\\*ia appendix.*", replacement = "", x = txt_short,
                  ignore.case = TRUE),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

@@

```{r}
a <- amicus %>%
  mutate(appendix_1a = str_count(txt_short, "\\*1a Appendix|\\*1A APPENDIX|\\*1A Appendix"))

@@

Let's see how many documents have `APPENDIX A` in them.
```{r}
amicus$appendix_a <- ifelse(amicus$appendix_1a < 1, str_count(amicus$txt_short, "APPENDIX A"), 0)

table(amicus$appendix_a)
```

`APPENDIX A` occurs in 56 briefs that did not already have the appendix removed.

@@

```{r}
amicus %>% filter(appendix_a > 0) %>% select(id, appendix_a)
```

@@

```{r}
amicus <- amicus %>% mutate(
         txt_short = case_when(
           appendix_1a == 0 &
           grepl("APPENDIX A", txt_short) ~ 
             gsub(pattern = "APPENDIX A.*", replacement = "", x = txt_short),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

@@

```{r}
a <- amicus %>% filter(appendix_1a == 0) %>%
  mutate(appendix_a = str_count(txt_short, "APPENDIX A"))

@@

```{r}
amicus$appendix <- ifelse(amicus$appendix_1a < 1 & amicus$appendix_a < 1, 
                            str_count(amicus$txt_short, "APPENDIX"), 0)

table(amicus$appendix)
```

There are still 86 briefs that mention `APPENDIX`. We want to manually look at some of the briefs that mention `APPENDIX` to see if they refer to the beginning of the appendix

```{r}
amicus %>% filter(appendix > 1) %>% select(id, appendix)
```

@@

```{r}
amicus <- amicus %>% mutate(
         txt_short = case_when(
           appendix_1a == 0 & appendix_a == 0 &
           grepl("APPENDIX", txt_short) ~ 
             gsub(pattern = "APPENDIX.*", replacement = "", x = txt_short),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

@@

```{r}
a <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0) %>%
  mutate(appendix = str_count(txt_short, "APPENDIX"))

@@

```{r}
a <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>%
  mutate(Appendix = str_count(txt_short, "Appendix"),
         appendix_all = str_count(txt_short, "appendix"))

@@

```{r}
amicus <- amicus %>% mutate(txt_short = str_to_lower(txt_short))
```

@@

```{r}
amicus <- amicus %>%
  mutate(footnotes = str_count(txt_short, "footnotes"))

table(amicus$footnotes)
```

@@

```{r}
amicus <- amicus %>%
  mutate(footnotes_cor = str_count(txt_short, "footnotes counsel of record"),
         footnotes_1 = str_count(txt_short, "footnotes 1"))

table(amicus$footnotes_cor)
```

```{r}
table(amicus$footnotes_1)
```

@@

```{r}
amicus <- amicus %>% mutate(
         txt_short = case_when(
           grepl("footnotes counsel of record", txt_short)
           & (id %in% footnotes_ids$id) ~ 
             gsub(pattern = "footnotes counsel of record.*", replacement = "", x = txt_short),
           grepl("footnotes 1", txt_short)
           & (id %in% footnotes_ids$id | id == '861814132010') ~ 
             gsub(pattern = "footnotes 1.*", replacement = "", x = txt_short),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

@@

```{r}
a <- amicus %>%
  mutate(footnotes_cor = str_count(txt_short, "footnotes counsel of record"),
         footnotes_1 = str_count(txt_short, "footnotes 1"))

@@

```{r}
table(a$footnotes_cor)
```

@@

```{r}
amicus$footnotes_star <- ifelse(amicus$footnotes_cor < 1 & amicus$footnotes_1 < 1,
                                str_count(amicus$txt_short, "footnotes \\*"), 0)

table(amicus$footnotes_star)
```

@@

```{r}
amicus <- amicus %>% mutate(
         txt_short = case_when(
           grepl("footnotes \\*", txt_short) ~ 
             gsub(pattern = "footnotes \\*.*", replacement = "", x = txt_short),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

@@

```{r}
a <- amicus %>%
  mutate(footnotes_star = str_count(txt_short, "footnotes \\*"))

@@

```{r}
a <- amicus %>% filter(footnotes_cor == 0 & footnotes_1 == 0 & footnotes_star == 0 &
                        appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>% 
  mutate(footnotes = str_count(txt_short, "footnotes"))

@@

```{r}
a <- amicus %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>% 
   mutate(appendix_all = str_count(txt_short, "appendix"))

@@

There are only 62 briefs remaining that mention an appendix that have not already had their appendix removed.

```{r}
#saving these ids to a csv
appendix_not_removed <- a %>% filter(appendix_all > 0) %>% select(id)

#box_write(appendix_not_removed,
#          file_name = "appendix-not-removed.csv",
#          dir_id = 145990409196)
```

Hoe many briefs had neither an appendix or footnotes removed?

```{r}
amicus %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0 &
                   footnotes_cor == 0 & footnotes_1 == 0 & footnotes_star == 0) %>% count()
```
253 briefs had neither an appendix or footnotes removed.

We manually went in and added the string "mnopqrst" to all briefs in which 'footnotes' and/or 'appendix' was found but not removed. We can now removed all text after this random string. There are two exceptions below that due to being pdfs that we could not edit, we will handle separately.

Case | Brief Name | ID | Text 
-- | -- | -- | --
WWH v Hellerstedt | Whole Women's Health v Hellerstedt. Amicus brief for Respondents by Physicians with Experience Treating Women in Rural or Emergency Settings.pdf | 861822669887 | Listing of Amici Physicians with Experience Treating Women in Rural or Emergency Settings
WWH v Hellerstedt | Whole Women's Health v Hellerstedt. Amicus brief for Respondents by Right to Life Advocates, Inc.pdf | 861824109102 | App. 1

```{r}
counts <- amicus %>%
  mutate(manual = str_count(txt_short, 'mnopqrst'))

table(counts$manual)
```

```{r}
amicus <- amicus %>% mutate(
         txt_short = case_when(
           grepl("mnopqrst", txt_short) ~ 
             gsub(pattern = "mnopqrst.*", replacement = "", x = txt_short),
           id == 861822669887 ~ gsub(pattern = "a-1 appendix.*", 
                    replacement = "", x = txt_short, ignore.case = TRUE),
           id == 861824109102 ~ gsub(pattern = "App. 1.*", 
                    replacement = "", x = txt_short, ignore.case = TRUE),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

Checking to make sure we did removed this text:

```{r}
counts <- amicus %>%
  mutate(manual = str_count(txt_short, 'mnopqrst'))

table(counts$manual)
```

```{r}
#amicus %>% filter(id == 861822669887) %>% pull(txt_short)
```

@@

```{r}
# amicus <- amicus %>% select(case, brief, id, txt_short)
# 
# box_write(amicus,
#           file_name = "shortened-amicus-brief-text.csv",
#           dir_id = 145990409196)
```

>>>>

---
title: "Shorten Litigant Text"
author: "Sarah Torrence and Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

# data
# data/processed litigant files/raw-litigant-brief-text.csv
litigant <- box_read("955333134918") %>% mutate(id = as.character(id))
```

@@

To pare down litigant text by removing unnecessary/irrelevant text.

@@

For most documents, there exists the header "summary of argument." If it did not exist, it was manually entered into the document. This represents the point at which the brief starts discussing their argument. We don't need text prior to this, as it's mainly intro information about the case and/or the authors.

Remove text before summary of argument. Run 2x in the event of a table of contents.

```{r}
# remove text after "summary of argument" if it exists
litigant <- litigant %>%
  mutate(txt_full = str_squish(txt_full),
         txt_short = case_when(
           id %in% c(955404304453, 955405038378) ~ txt_full,
           grepl("summary of argument", txt_full, ignore.case = TRUE) ~
             gsub(pattern = ".*summary of argument",
                  replacement = "", x = txt_full, ignore.case = TRUE),
           grepl("summary of the argument", txt_full, ignore.case = TRUE) ~
             gsub(pattern = ".*summary of the argument", replacement = "", x = txt_full, ignore.case = TRUE),
           grepl("mnopqrst", txt_full, ignore.case = T) ~
             gsub(pattern = ".*mnopqrst", replacement = "", x = txt_full, ignore.case = T),
           T ~ txt_full),
         txt_short = str_squish(txt_short))
```

@@

```{r}
litigant %>% filter(txt_short == "") %>% select(-txt_full)
#litigant %>% filter(txt_short == txt_full)
```

@@

```{r}
#litigant %>% sample_n(1) %>% pull(id, txt_short)
```

@@

```{r}
litigant <- litigant %>%
  mutate(txt_short = str_squish(txt_short),
    appendix_1a = str_count(txt_short, "\\*1a Appendix|\\*1A APPENDIX|\\*1A Appendix|\\*IA APPENDIX"))
```

@@

```{r}
table(litigant$appendix_1a)
```

@@

```{r}
litigant <- litigant %>% mutate(
         txt_short = str_squish(txt_short),
         txt_short = case_when(
           grepl("\\*1a appendix|\\*ia appendix", txt_short, ignore.case = TRUE) ~ 
             gsub(pattern = "\\*1a appendix.*|\\*ia appendix.*", replacement = "", x = txt_short,
                  ignore.case = TRUE),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

@@

```{r}
a <- litigant %>%
  mutate(appendix_1a = str_count(txt_short, "\\*1a Appendix|\\*1A APPENDIX|\\*1A Appendix"))

@@

Let's see how many documents have `APPENDIX A` in them.
```{r}
litigant$appendix_a <- ifelse(litigant$appendix_1a < 1, str_count(litigant$txt_short, "APPENDIX A"), 0)

table(litigant$appendix_a)
```

`APPENDIX A` occurs in 2 briefs that did not already have the appendix removed.

@@

```{r}
litigant %>% filter(appendix_a > 0) %>% select(id, appendix_a)
```

@@

```{r}
litigant <- litigant %>% mutate(
         txt_short = case_when(
           appendix_1a == 0 &
           grepl("APPENDIX A", txt_short) ~ 
             gsub(pattern = "APPENDIX A.*", replacement = "", x = txt_short),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

@@

```{r}
a <- litigant %>% filter(appendix_1a == 0) %>%
  mutate(appendix_a = str_count(txt_short, "APPENDIX A"))

@@

```{r}
litigant$appendix <- ifelse(litigant$appendix_1a < 1 & litigant$appendix_a < 1, 
                            str_count(litigant$txt_short, "APPENDIX"), 0)

table(litigant$appendix)
```

We want to manually look at some of the briefs that mention `APPENDIX` to see if they refer to the beginning of the appendix. None mention appendix more than once, so we can skip below.

```{r}
litigant %>% filter(appendix > 1) %>% select(id, appendix)
```

@@

```{r}
litigant <- litigant %>% mutate(
         txt_short = case_when(
           appendix_1a == 0 & appendix_a == 0 &
           grepl("APPENDIX", txt_short) ~ 
             gsub(pattern = "APPENDIX.*", replacement = "", x = txt_short),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

@@

```{r}
a <- litigant %>% filter(appendix_1a == 0 & appendix_a == 0) %>%
  mutate(appendix = str_count(txt_short, "APPENDIX"))

@@

```{r}
a <- litigant %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>%
  mutate(Appendix = str_count(txt_short, "Appendix"),
         appendix_all = str_count(txt_short, "appendix"))

@@

```{r}
litigant <- litigant %>% mutate(txt_short = str_to_lower(txt_short))
```

@@

```{r}
litigant <- litigant %>%
  mutate(footnotes = str_count(txt_short, "footnotes"))

table(litigant$footnotes)
```

@@

```{r}
litigant <- litigant %>%
  mutate(footnotes_cor = str_count(txt_short, "footnotes \\* counsel of record"),
         footnotes_cor2 = str_count(txt_short, "footnotes fn \\* counsel of record"),
         footnotes_1 = str_count(txt_short, "footnotes 1"))

table(litigant$footnotes_cor)
table(litigant$footnotes_cor2)
```

```{r}
table(litigant$footnotes_1)
```

@@

```{r}
litigant <- litigant %>% mutate(
         txt_short = case_when(
           grepl("footnotes \\* counsel of record", txt_short) ~ 
             gsub(pattern = "footnotes \\* counsel of record.*", replacement = "", x = txt_short),
            grepl("footnotes fn \\* counsel of record", txt_short) ~ 
             gsub(pattern = "footnotes fn \\* counsel of record.*", replacement = "", x = txt_short),
           grepl("footnotes 1", txt_short) ~ 
             gsub(pattern = "footnotes 1.*", replacement = "", x = txt_short),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

@@

```{r}
a <- litigant %>%
  mutate(footnotes_cor = str_count(txt_short, "footnotes counsel of record"),
         footnotes_cor2 = str_count(txt_short, "footnotes \\* counsel of record"),
         footnotes_1 = str_count(txt_short, "footnotes 1"))

@@

```{r}
table(a$footnotes_cor)
table(a$footnotes_cor2)
```

@@

```{r}
litigant$footnotes_star <- ifelse(litigant$footnotes_cor < 1 & litigant$footnotes_1 < 1,
                                str_count(litigant$txt_short, "footnotes \\*"), 0)

table(litigant$footnotes_star)
```

@@

```{r}
litigant <- litigant %>% mutate(
         txt_short = case_when(
           grepl("footnotes \\*", txt_short) ~ 
             gsub(pattern = "footnotes \\*.*", replacement = "", x = txt_short),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

@@

```{r}
a <- litigant %>%
  mutate(footnotes_star = str_count(txt_short, "footnotes \\*"))

@@

```{r}
a <- litigant %>% filter(footnotes_cor == 0 & footnotes_1 == 0 & footnotes_star == 0 &
                        appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>% 
  mutate(footnotes = str_count(txt_short, "footnotes"))

@@

```{r}
a <- litigant %>% filter(appendix_1a == 0 & appendix_a == 0 & appendix == 0) %>% 
   mutate(appendix_all = str_count(txt_short, "appendix"))

@@

@@

```{r}
 litigant <- litigant %>% select(case, brief, id, brief_party, txt_short)

 box_write(litigant,
           file_name = "shortened-litigant-brief-text.csv",
           dir_id = 162588272045)
```

### 2022-05-10 data-cleaning/05-add-amicus-measures.Rmd
add litigant frames

# data/processed amicus files/amicus_clean_512_no_stride.csv
amicus_party <- box_read("942789542605") %>% select(id, brief_party) %>% distinct(id, brief_party)
# data/processed_amicus_files/amicus_clean_512_no_stride_split.csv
#amicus <- box_read("946701865033")
# data/processed_amicus_files/shortened_amicus_brief_text.csv
amicus <- box_read("910635411098")

>>>>

# data/processed amicus files/amicus_clean_512_no_stride.csv
amicus_party <- box_read("942789542605") %>% select(id, brief_party) %>% distinct(id, brief_party)

# data/processed_amicus_files/shortened_amicus_brief_text.csv
amicus <- box_read("910635411098")

### 2022-05-10 data-cleaning/06-clean-data-and-frame-dict.Rmd
add anders, small changes close #29
add litigant frames

To clean the amicus text and the frame dictionary for searching.

@@

@@

  return(df)

}

@@

@@

```{r}
# The clean_text function
clean_text_frames <- function(x) {

@@

```{r}
frames <- frames %>% distinct(frame, frame_code, word, word_clean)
```

>>>>

To clean the amicus and litigant text and the frame dictionary for searching.

@@

Litigant Text

```{r}
# data/processed litigant files/shortened-litigant-brief-text.csv
litigant <- box_read("955499186926") %>% rename(text = txt_short)
```

@@

  return(df)
}

@@

# Litigant Brief Cleaning

```{r}
# fix characters on text
litigant <- litigant %>% mutate(text_clean = fix_chars(text))

# rmv urls
litigant <- litigant %>%
  mutate(text_clean = qdapRegex::rm_url(text_clean))

# rmv proper names & replace w/underscores
litigant <- litigant %>% as.data.frame()
litigant <- DataCombine::FindReplace(data = litigant, Var = "text_clean", 
                         replaceData = proper_names, 
                         from = "word", to = "replacement", exact = FALSE)

# rmv "the fact that" & "in fact"
litigant <- litigant %>% mutate(text_clean = gsub("the fact that|in fact", "", text_clean))

# rmv facts & reports in specific cases
litigant <- litigant %>%
  mutate(
    text_clean = case_when(
      case == "City of Akron v Akron Center" ~ 
        gsub(pattern = "fact |facts ", replacement = "", x = text_clean, ignore.case = T),
      case %in% c("Planned Parenthood Assoc of Kansas City, MO v Ashcroft, Attorn Gen of MO",
                  "Thornburgh v. American College of OBGYNs") ~
        gsub(pattern = "report|reports|reporting|reported", replacement = "", x = text_clean, ignore.case = T),
      TRUE ~ text_clean
    )
  )

# clean text
litigant <- clean_text(litigant)

# save only necessary cols
litigant <- litigant %>% select(case:brief_party, text_clean)

# check no NAs
litigant %>% filter(is.na(text_clean))
```

```{r}
box_write(litigant,
           file_name = "clean-shortened-litigant-text.csv",
           dir_id = 162588272045)
```

@@

# The clean_text function
clean_text_frames <- function(x) {

@@

```{r}
frames <- frames %>% distinct(frame, frame_code, word_clean)
```

### 2022-05-10 data-cleaning/08-create-regression-data.Rmd
add litigant frames

case_amici_level <- box_read("947450386335")
justice_level <- box_read("947810760828")
```

@@

To create regression data for Amicus IV. The dependent variable is justicevot. The controls are: justicemq, justicefem, nonftyp2, lcdisdirfem. The independent vars are the framing measures.

@@

```{r}
justice_level <- justice_level %>% 
  filter(
    !grepl("Menillo|Guste|Hartigan|Mazurek|Benten|Lambert|Leavitt|Gerstein", casename)) %>% 
  select(case = casename, ddate2,
         justiceid, justicevot, justicemq, justicefem,
         nonftyp2, lcdisdirfem, cirsplit,
         cfemam, coppam, pfemam, poppam)

@@

@@

```{r}
# start with justice_level bc this df has cases that the case_level does not
# these cases don't have amicus briefs, which is why they aren't in our data
final <- justice_level %>% 
  left_join(., case_level, by = "case") %>% 
  select(case, ddate2:poppam, everything())

>>>>

# amici frames
case_amici_level <- box_read("947450386335")

# litigant frames (already one row per case)
litigant_case_level <- box_read("955507061348") %>%
  select(case, contains("freq")) %>% 
  rename_with(.cols=contains("freq"), .fn=~sub("_freq.*", "", .x))

# justice level data
justice_level <- box_read("947810760828")
```

@@

To create regression data for Amicus IV. The dependent variable is justicevot. The controls are: justicemq, justicefem, nonftyp2, lcdisdirfem, . The independent vars are the framing measures.

@@

```{r}
justice_level <- justice_level %>% 
  filter(
    !grepl("Menillo|Guste|Hartigan|Mazurek|Benten|Lambert|Leavitt|Gerstein", casename)) %>% 
  select(case = casename, ddate2,
         justiceid, justicevot, justicemq, justicefem, sgfem3,
         nonftyp2, lcdisdirfem, cirsplit,
         cfemam, coppam, pfemam, poppam)

@@

litigant_case_level <- litigant_case_level %>% 
  mutate(case = str_replace(case, 'v\\.', 'v'),
         case = str_replace_all(case, "(,|’|'|\\)|\\()", ""),
         case = case_when(
           case == "Anders Solicitor of Richland County v Floyd" ~ "Anders v Floyd",
           case == "Ayotte v Planned Parenthood of Northern New England" ~ "Ayotte v PP",
           case == "City of Akron v Akron Center for Rep Health" ~ "City of Akron v Akron Center",
           case == "Gonzales v Planned Parenthood Federation of America" ~ "Gonzales v PP",
           case == "Hill et al v Colorado" ~ "Hill v Colorado",
           case == "Judy Madsen v Womens Health Center" ~ "Madsen v Womens Health Center",
           case == "NOW v Joseph Scheidler 1994" ~ "NOW v Scheidler 1994",
           case == "Ohio v Akron Center for Reproductive Health" ~ "Ohio v Akron Center",
           case == "Planned Parenthood Assoc of Kansas City MO v Ashcroft Attorn Gen of MO" ~
             "PP v Ashcroft",
           case == "Planned Parenthood of Southeastern Pennsylvania v Casey" ~ "PP v Casey",
           case == "Planned Parenthood of Central MO v Danforth" ~ "PP v Danforth",
           case == "Joseph Scheidler v NOW 2003" ~ "Scheidler v NOW 2003",
           case == "Joseph Scheidler v NOW 2006" ~ "Scheidler v Now 2006",
           case == "Schenck et al v Pro-Choice Network of Western NY" ~
             "Schenck v Pro-Choice Network",
           case == "Thornburgh v American College of Obstetricians and Gynecologists LDEF" ~
             "Thornburgh v American College of OBGYNs",
           case == "Whole Womens Health v Hellerstedt 2016" ~ "WWH v Hellerstedt",
           T ~ case
         ))

@@

```{r}
# start with justice_level bc this df has cases that the case_level does not
# these cases don't have amicus briefs, which is why they aren't in our data
final <- justice_level %>% 
  left_join(., case_level, by = "case") %>% 
  left_join(., litigant_case_level, by = "case") %>% 
  select(case, ddate2:poppam, everything())
